Carbonate chemistry at Ny-Ålesund

### 2021-02-19 awipev-CO2.Rmd

# Good data per year

#rm(d_min)
```

>>>>

# Monthly distribution of hourly data
d2 <- d_all %>% 
  dplyr::select(datetime, montht, pco2_inst, ph_s_sf_temp_insi)
p <- ggplot(data = d2, aes(x = montht, y = pco2_inst)) +
  geom_bar(stat="identity", width = 0.3) +
  scale_fill_discrete(labels = labels) + 
  labs(x="Month", y="pCO2", title = "") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
p
ggsave(filename = "figures/monthly_availability.png", plot = p, width = 20, units = "cm")
#rm(d_min, d2)
```
